A Road Segment Prioritization Approach for Cycling Infrastructure

### 2023-04-24 README.Rmd
add wysling+purves citation

The above points are accounted for by using a weighted road network for
routing. This has been previously done by multiplying all road segments
without cycling infrastructure by a fixed impedance factor
[@mauttone2017bicycle], or by assigning different weights to the road
segments proportional to the investment cost of bringing them to an
acceptable level of stress for cycling [@duthie2014optimization].
Perceived stress for cyclists has been found to be a function of vehicular traffic
volume and speed [@sorton1994bicycle], both of which vary predictably
with road type. @gehrke2020cycling build on this information to use
routing impedance factors for road segments that are based on road type
and the existence of cycling infrastructure.

For the purposes of this paper we created a similar weighting profile
that is adjusted to favor less stressful roads (based on the definition
by @sorton1994bicycle and information from Table
\@ref(table:osmroadtypes)) and roads with existing cycling
infrastructure. We believe this to be more appropriate than the simplistic
approach adopted by @mauttone2017bicycle as it makes use of a hierarchy
of road preference based on perceived stress levels, going beyond simply
favouring roads with existing cycling infrastructure.

>>>>

The above points are accounted for by using a weighted road network for
routing. This has been previously done by multiplying all road segments
without cycling infrastructure by a fixed impedance factor
[@mauttone2017bicycle], by assigning different weights to the road
segments that are (a) proportional to the investment cost of bringing them to an
acceptable level of stress for cycling [@duthie2014optimization], or (b) inversely proportional to 
perceived level of stress experienced by cyclists [@wysling2022improve].
Perceived stress for cyclists has been found to be a function of vehicular traffic
volume and speed [@sorton1994bicycle], both of which vary predictably
with road type. @gehrke2020cycling build on this information to use
routing impedance factors for road segments that are based on road type
and the existence of cycling infrastructure.

For the purposes of this paper we created a similar weighting profile
that is adjusted to favor less stressful roads (based on the definition
by @sorton1994bicycle and information from Table
\@ref(table:osmroadtypes)) and roads with existing cycling
infrastructure. We believe this to be more appropriate than the simplistic
approach adopted by @mauttone2017bicycle as it makes use of a hierarchy
of road preference based on perceived stress levels, going beyond simply
favouring roads with existing cycling infrastructure. 
It is also different to the weighting profile used by @wysling2022improve as it adds a larger
weight on trunk and primary roads then other roads without cycling infrastructure.
